Nodal Discontinuous Galerkin Method for the Two-Moment Model of Neutrino Transport

### 2017-07-20 Documents/M1/dgM1Curvilinear.tex
Keep updates.

\section{Two-Moment Model for Neutrino Transport}

@@

%\ee{Ran write about tabulated B85 absorption and scattering opacities.}
In this section, we bring the speed of light $c$ back.

The total opacity $\kappa(\epsilonNu,\bU)=\tilde{\chi}(\epsilonNu,\bU)+\sigma(\epsilonNu,\bU)$, where $\tilde{\chi}(\epsilonNu,\bU)$ is the absorption opacity of neutrino and  $\sigma(\epsilonNu,\bU)$ is the scattering opacities. 
The absorption opacity of neutrino $\tilde{\chi}(\epsilonNu,\bU)$ 
\begin{equation}
  \tilde{\chi}(\epsilonNu,\bU) = \chi(\epsilonNu,\bU) + \eta(\epsilonNu,\bU), 
\end{equation}
 is the sum of the neutrino emissivity $\eta(\epsilonNu,\bU) $ and the neutrino absorptivity  $ \chi(\epsilonNu,\bU)$. The scattering opacities $\sigma(\epsilonNu,\bU)$ contains isoenergetic scattering opacities, neutrino-electron scattering opacities and have a integral form in the Boltzmann equation: if we include emission, absorption, isoenergetic scattering of neutrino by nucleons and nuclei, and neutrino electron scattering, the simplified Boltzmann equation is

@@

The third and fourth terms are contributions from isoenergetic scattering of neutrino by nucleons and nuclei. The last two terms are contributions from neutrino-electron scattering.

@@

\subsection{The isoenergetic scattering kernel}
The isoenergetic scattering kernel $R_{\IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU)$ has the following relation:
\begin{align}
R_{\IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) & = R_{\IS}^{nucleons}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) +  R_{\IS}^{nuclei}(\mu_0, \mu^\prime_0, \epsilonNu,\bU),
\end{align}
where
\begin{align}
\cos\theta = \mu_0\mu^\prime_0 + [(1-\mu_0^2)(1-\mu_0^{\prime 2})]^{1/2}\cos\theta,
\end{align}
and
\begin{align}
R_{\IS}(\cos\theta, \epsilonNu, \bU) = R^{nucleons}(\cos\theta,\epsilonNu, \bU) + R^{nuclei}_{\IS}(\cos\theta, \epsilonNu, \bU)
\end{align}
where $R^{nucleons}_{\IS} (\cos\theta,\epsilonNu, \bU)$ and $R^{nuclei}_{\IS}(\cos\theta,\epsilonNu,\bU)$ are given by Eq. (35) and Eq. (36) in \citet{mezzacappaBruenn_1993a}.

Expanding the isoenergetic scattering kernel in the first two terms of a Legendre series yields
\begin{align}
R_{\IS}(\omega, \omega, \cos\theta) \approx \dfrac{1}{2} \Phi_{0,\IS}(\omega) + \dfrac{3}{2}\Phi_{1,\IS}(\omega)\cos\theta
\end{align}

@@

>>>>

\section{Two-Moment Model for Neutrino Transport}
\label{sec:twoMomentModel}

@@

In this section, we bring the speed of light $c$ back.

As we mentioned in Section~\ref{sec:twoMomentModel}, the total opacity $\kappa(\epsilonNu,\bU)=\tilde{\chi}(\epsilonNu,\bU)+\sigma(\epsilonNu,\bU)$.
The absorption opacity of neutrino $\tilde{\chi}(\epsilonNu,\bU)$ is the sum of the neutrino emissivity $\eta(\epsilonNu,\bU) $ and the neutrino absorptivity  $ \chi(\epsilonNu,\bU)$:
\begin{equation}
  \tilde{\chi}(\epsilonNu,\bU) = \eta(\epsilonNu,\bU) + \chi(\epsilonNu,\bU). 
\end{equation}
 The scattering opacities $\sigma(\epsilonNu,\bU)$ contains (isotropic) elastic scattering opacities, neutrino-electron scattering opacities and have a integral form in the Boltzmann equation: the simplified Boltzmann equation is

@@

The third and fourth terms are contributions from (isotropic) elastic scattering of neutrino by nucleons and nuclei. The last two terms are contributions from neutrino-electron scattering.

@@

\subsection{The isotropic elastic scattering kernel}
The isotropic elastic scattering kernel $R_{\IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU)$ has the following relation:
\begin{align}
R_{\IS}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) & = R_{\IS}^{nucleons}(\mu_0, \mu^\prime_0, \epsilonNu,\bU) +  R_{\IS}^{nuclei}(\mu_0, \mu^\prime_0, \epsilonNu,\bU),
\end{align}
where
\begin{align}
\cos\theta = \mu_0\mu^\prime_0 + [(1-\mu_0^2)(1-\mu_0^{\prime 2})]^{1/2}\cos\theta,
\end{align}
and
\begin{align}
R_{\IS}(\cos\theta, \epsilonNu, \bU) = R^{nucleons}(\cos\theta,\epsilonNu, \bU) + R^{nuclei}_{\IS}(\cos\theta, \epsilonNu, \bU)
\end{align}
where $R^{nucleons}_{\IS} (\cos\theta,\epsilonNu, \bU)$ and $R^{nuclei}_{\IS}(\cos\theta,\epsilonNu,\bU)$ are given by Eq. (35) and Eq. (36) in \citet{mezzacappaBruenn_1993a}.

Expanding the isotropic elastic scattering kernel in the first two terms of a Legendre series yields
\begin{align}
R_{\IS}(\omega, \omega, \cos\theta) \approx \dfrac{1}{2} \Phi_{0,\IS}(\omega) + \dfrac{3}{2}\Phi_{1,\IS}(\omega)\cos\theta
\end{align}

@@

The isotropic term $\dfrac{1}{2}\Phi_{0,\NES}^{\In/\Out}(\omega,\omega^{\prime}, \bU)$ is the $R^{\In}$ and $R^{\Out}$  in Eqs.~\eqref{eq:momentEquationEnergy} and \eqref{eq:momentEquationMomentum}.
